---
title: "First_File"
author: "Barry DeCicco"
date: '2022-05-05'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This repo is to practice interrupted time series analysis, as in:
https://www.statmethods.net/advstats/timeseries.html

# Load Libraries

```{r load-libraries}
library(tidyverse)
library(forecast)

```

# Create Data

The ts() function will convert a numeric vector into an R time series object. The format is ts(vector, start=, end=, frequency=) where start and end are the times of the first and last observation and frequency is the number of observations per unit time (1=annual, 4=quartly, 12=monthly, etc.).


```{r create-data}

myvector <- rnorm(72,0,1)

# save a numeric vector containing 72 monthly observations
# from Jan 2009 to Dec 2014 as a time series object
myts <- ts(myvector, start=c(2009, 1), end=c(2014, 12), frequency=12)

# subset the time series (June 2014 to December 2014)
myts2 <- window(myts, start=c(2014, 6), end=c(2014, 12))

# plot series
plot(myts)



```
# Seasonal Decomposition:

```{r seasonal-decomposition}


# Seasonal decomposition
fit <- stl(myts, s.window="period")
plot(fit)

# additional plots
monthplot(myts)

seasonplot(myts) 

```



















